Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
making it work

	\input{tables/cl_table_1}
\end{table}

\subsection{Fast updates in reinforcement learning}

\begin{figure}[!t]
  \centering
  \begin{subfigure}{.2\textwidth}
  \resizebox{\textwidth}{!}{%
  \begin{tikzpicture}[inner sep=0,outer sep=0]

    % Draw decorated 'ground'
    \draw[postaction={draw, decorate, decoration={border, angle=-45,
					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);

    % The cart
    \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
    \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};

    % Wheels
    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};

    % The arm
    \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
    \node[fill=black,circle,minimum size=.5cm] at (dot) {};

    % Markings
    \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);

    % Arrow
    \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);

    \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }

    % Draw arc
    \centerarc[black,line width=3pt](dot)(270:290:11)
    \node at (6.5,-9) {$\theta$};

    \node[white,minimum size=1cm] at (4.5,-13) {};

  \end{tikzpicture}}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.78\textwidth}
    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};

    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
    \input{./fig/rl}

  \end{subfigure}
  \hfill
  \caption{Add caption.}
  \label{fig:rl}
\end{figure}

@@

\subsection{Problem Statement and Background} \label{sec:problem-statement}
We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
iid noise \(\noise_{t}\), given by,
\begin{align}
\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
\end{align}
\begin{assumption}
  (system properties) The environment's dynamics are $L_{\transitionFn}\text{-Lipschitz}$ continuous and the transition noise $\noise_{t}$ is $\sigma\text{-sub-Gaussian}$ for all $t \geq 0$.
\end{assumption}

\subsection{Model-based Reinforcement Learning (RL)}
The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
rewards in expecation under the transition noise (aleatoric uncertainty),
\begin{align} \label{eq-model-free-objective}
\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right],
\end{align}
where $\gamma \in [0, 1]$

\textbf{Model-based}
In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
\cref{alg-mbrl} shows the typical model-based RL loop.
Importantly, the dynamics are usually only updated after an episode $i$.

\begin{algorithm}[!b]
\caption{Model-based RL}\label{alg-mbrl}
\begin{algorithmic}[1]
  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
      % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-ucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
      % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
    \EndFor
    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
    % \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$ using $\dataset_{0:i+1}$
    % \State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
    \State Improve policy $\pi_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
    %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
\EndFor
\end{algorithmic}
\end{algorithm}

% \begin{minipage}{0.499\textwidth}
% \begin{algorithm}[H]
% \caption{Model-based RL}\label{alg-mbrl}
% \begin{algorithmic}[1]
%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
%     \EndFor
%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
%     \State Improve policy $\pi_{i+1}$
%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
% \EndFor
% \end{algorithmic}
% \end{algorithm}
% \end{minipage}
% \hfill
% \begin{minipage}{0.499\textwidth}
% \begin{algorithm}[H]
% \caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
% \begin{algorithmic}[1]
%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
%     % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
%       % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
%       \State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
%     \EndFor
%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
%     \State Improve policy $\pi_{i+1}$
%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
% \EndFor
% \end{algorithmic}
% \end{algorithm}
% \end{minipage}

\subsection{Exploration Strategies}
\textbf{Greedy exploitation}
Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
\begin{align} \label{eq-greedy}
\policy_{i+1}^{\text{greedy}} = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\transitionFn \sim p(\transitionFn \mid \dataset_{0:i})} \left[ J(\transitionFn, \policy) \right],
\end{align}
This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC
\cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
This approach helps to alleviate model bias as the posterior ``knows what the model does not know''.
This is because the predictive posterior \(p(f(s_{t},a_{t}) \mid (s_{t},a_{t}),  \mathcal{D} )\) will be (or should be) uncertain when making
predictions far away from the training data.
The expectation considers all possible dynamics models which prevents the policy optimisation from
exploiting innacuracies in the model.
This approach has no guarantees for exploration in the general case.
However, under specific dynamics and reward structures (e.g. PILCO) this objective can achieve sublinear regret.
\todo{need to double check sublinear regret statement. And give a reference}

\textbf{Posterior sampling}
\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
\begin{align} \label{eq-posterior-sampling}
\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
\end{align}

\textbf{Hallucinated upper confidence RL}
A more theoretically grounded exploration strategy is UCRL \citep{jakschNearoptimal2010}, which optimises joinly over
policies and models inside the set
\(\mathcal{M} = \{ f \mid | f(s,a) - \mu_{i}(s, a) | \leq \beta_{i} \Sigma_{i}(s, a) \quad \forall s, a \in \mathcal{S} \times \mathcal{A} \}\), representing all statistically plausible
models under the posterior \(p(f(s,a) \mid \mathcal{D}_{0:i} \cup (s,a)) = \mathcal{N}(f(s,a) \mid \mu_{i}(s,a), \Sigma_{i}(s,a))\) at episode \(i\).
This strategy is given by,
\begin{align} \label{eq-ucrl}
\policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
\end{align}
This strategy optimises an optimistic policy over the set of plausible dynamics models.
Although this joint optimisation is intractable in general,
\cite{curiEfficient2020} proposed a practical alternative which is detailed in \cref{sec-hucrl}.

\textbf{MPC vs policy learning}
It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-ucrl} can be used with both model predictive control (MPC)
techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).

In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
for example, model bias and the exploration-exploitation trade-off.

\todo{show how to get new $\dualParam{1}$ and $\dualParam{2}$ in Train dynamics line of \cref{alg-mbrl-fast-updates}}
\begin{algorithm}[!t]
\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
\begin{algorithmic}[1]
  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$ (inc. dual parameters $\dualParam{1}, \dualParam{2}$), policy $\policy_{0}$
    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
      % \State Execute policy $\policy_{i}(\state_{t})$ (\cref{eq-fast-update-mpc}) in environment
      \State Use \cref{eq-fast-update-mpc} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy^{\text{fast}}_{i}(\state_{t})), r_{t+1})$
      % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
      % \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
      %\State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
      \State {\color{blue}Update dynamics posterior using \cref{eq-dual-update-svgp}, i.e. fast update}
      % \begin{align}
      % \dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
      % \dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
      % \end{align}}
    \EndFor
    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
    \State Improve policy $\pi^{\text{fast}}_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
\EndFor
\end{algorithmic}
\end{algorithm}

\subsubsection{Fast updates}

In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
\citep{khanApproximate2019} to formulate a function space SVGP posterior,
where we can apply the fast updates from \cref{eq-dual-update-svgp}.
At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
We then linearise our BNN around the optimal parameters and interpret it as a GP.
Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.

>>>>

	\input{tables/cl_table_1}
\end{table}
%
%
%\subsection{Fast updates in reinforcement learning}
%
%\begin{figure}[!t]
%  \centering
%  \begin{subfigure}{.2\textwidth}
%  \resizebox{\textwidth}{!}{%
%  \begin{tikzpicture}[inner sep=0,outer sep=0]
%  
%    % Draw decorated 'ground'
%    \draw[postaction={draw, decorate, decoration={border, angle=-45,
%					amplitude=1cm, segment length=.5cm}}] (-3,-1.5) -- (12,-1.5);
%  
%    % The cart
%    \draw[draw=black,fill=black!50,draw=black,line width=3pt,rounded corners=1mm] (0,0) rectangle (9cm,3cm);
%    \node[fill=black,circle,minimum size=.5cm] (dot) at (4.5cm,3cm) {};
%    
%    % Wheels
%    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,,fill=black!50] at (2cm,-.5cm) {};
%    \node[fill=white,draw=black,line width=3pt,circle,minimum size=2cm,fill=black!50] at (7cm,-.5cm) {};  
%    
%    % The arm
%    \node[anchor=north,minimum width=1cm,minimum height=14cm,draw=black,rotate=20,rounded corners=5mm,yshift=7mm,xshift=-.3mm,fill=white,draw=black,line width=3pt] at (dot) {};
%    \node[fill=black,circle,minimum size=.5cm] at (dot) {};
%    
%    % Markings
%    \draw[loosely dashed,line width=1pt] (4.5,6) -- (4.5,-10);
%    
%    % Arrow
%    \draw[->,black,line width=3pt,-{Latex[length=7mm,width=7mm]}] (1,5) --node[above,outer sep=6pt]{\large $x$} (4.5,5);
%    
%    \def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
%    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
%    
%    % Draw arc
%    \centerarc[black,line width=3pt](dot)(270:290:11)
%    \node at (6.5,-9) {$\theta$};
%    
%    \node[white,minimum size=1cm] at (4.5,-13) {};
%    
%  \end{tikzpicture}}
%  \end{subfigure}
%  \hfill
%  \begin{subfigure}{.78\textwidth}
%    % \tikz\node[minimum width=\textwidth,minimum height=.35\textwidth,fill=black!10,rounded corners=2pt]{RL trjectories or something interesting?};
%
%    % \includegraphics[width=0.5\textwidth]{./fig/rl.pdf}
%    \input{./fig/rl}
%
%
%  \end{subfigure}
%  \hfill
%  \caption{Add caption.}
%  \label{fig:rl}
%\end{figure}
%
%

@@

\subsection{Problem Statement and Background} \label{sec:problem-statement}
We consider environments with states \(\state \in \stateDomain \), actions \(\action \in \actionDomain\) and transition dynamics \(\transitionFn: \stateDomain \times \actionDomain \rightarrow \stateDomain \) subject to
iid noise \(\noise_{t}\), given by,
\begin{align}
\state_{t+1} = \transitionFn(\state_{t}, \action_{t}) + \noise_{t}.
\end{align}
\begin{assumption}
  (system properties) The environment's dynamics are $L_{\transitionFn}\text{-Lipschitz}$ continuous and the transition noise $\noise_{t}$ is $\sigma\text{-sub-Gaussian}$ for all $t \geq 0$.
\end{assumption}
%\subsection{Model-based Reinforcement Learning (RL)}
%The goal of reinforcement learning is to find a policy \(\pi \in \Pi\) that maximises the sum of discounted
%rewards in expecation under the transition noise (aleatoric uncertainty),
%\begin{align} \label{eq-model-free-objective}
%\policy^{*} = \arg \max_{\policy \in \policyDomain} J(\transitionFn, \policy) = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\noise_{0:\infty}} \left[ \sum_{t=0}^{\infty} \discount^{t} \rewardFn(\state_{t},\action_{t}) \right],
%where $\gamma \in [0, 1]$
%\textbf{Model-based}
%In Bayesian model-based RL, we obtain the posterior over the dynamics \(p(f\mid\mathcal{D})\) after performing (approximate) Bayesian
%inference given a state transition data set \(\mathcal{D} = \{\{(s_{t},a_{t}), s_{t+1}\}^{T_{i}}_{t=1}\}_{i=0}^{N}\).
%\cref{alg-mbrl} shows the typical model-based RL loop.
%Importantly, the dynamics are usually only updated after an episode $i$.
%\begin{algorithm}[!b]
%\caption{Model-based RL}\label{alg-mbrl}
%\begin{algorithmic}[1]
%  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
%\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
%    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
%    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
%      % \State Collect  $\tau_{0:t} = \tau_{0:t-1} \cup (\state_{j}, \action_{j}, \state_{j+1}, r_{j+1})$
%      \State Use \cref{eq-greedy}/\cref{eq-posterior-sampling}/\cref{eq-ucrl} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy_{i}(\state_{t})), r_{t+1})$
%      % \State Execute policy $\policy_{i}(\state_{t})$ in environment and update trajectory $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
%    \EndFor
%    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
%    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
%    % \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$ using $\dataset_{0:i+1}$
%    % \State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
%    \State Improve policy $\pi_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
%    %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
%\EndFor
%\end{algorithmic}
%\end{algorithm}
%% \begin{minipage}{0.499\textwidth}
%% \begin{algorithm}[H]
%% \caption{Model-based RL}\label{alg-mbrl}
%% \begin{algorithmic}[1]
%%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
%% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
%%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
%%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
%%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
%%     \EndFor
%%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
%%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
%%     \State Improve policy $\pi_{i+1}$
%%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
%% \EndFor
%% \end{algorithmic}
%% \end{algorithm}
%% \end{minipage}
%% \hfill
%% \begin{minipage}{0.499\textwidth}
%% \begin{algorithm}[H]
%% \caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
%% \begin{algorithmic}[1]
%%   \Require Initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$, policy $\policy_{0}$
%%     % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
%% \For{$i  \in \{0, 1, \ldots, \text{num episodes} \}$}
%%     \For{$t  \in \{0, 1, \ldots, \text{num steps} \}$}
%%       \State Execute policy $\policy_{i}(\state_{t})$ in environment
%%       % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
%%       \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
%%       \State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
%%     \EndFor
%%     \State Update data set $\mathcal{D}_{0:i+1} = \mathcal{D}_{0:i} \cup \tau_{i+1}$
%%     \State Train dynamics $p(\transitionFn \mid \dataset_{0:i+1})$
%%     \State Improve policy $\pi_{i+1}$
%%     %\State Improve policy $\pi_{i+1}$ using $p(\transitionFn \mid \dataset_{0:i+1})$ and/or $\dataset_{0:i+1}$
%% \EndFor
%% \end{algorithmic}
%% \end{algorithm}
%% \end{minipage}
%\subsection{Exploration Strategies}
%\textbf{Greedy exploitation}
%Given the posterior dynamics \(p(\transitionFn \mid \mathcal{D})\),
%a common approach is to simply take the expecation over both the aleatoric and epistemic uncertainty,
%\begin{align} \label{eq-greedy}
%\policy_{i+1}^{\text{greedy}} = \arg \max_{\policy \in \policyDomain} \mathbb{E}_{\transitionFn \sim p(\transitionFn \mid \dataset_{0:i})} \left[ J(\transitionFn, \policy) \right],
%This approach has been widely adopted, for example, in PILCO, PETS, GP-MPC
%\cite{deisenrothPILCO2011,chuaDeepReinforcementLearning2018,kamtheDataEfficient2018}.
%This approach helps to alleviate model bias as the posterior ``knows what the model does not know''.
%This is because the predictive posterior \(p(f(s_{t},a_{t}) \mid (s_{t},a_{t}),  \mathcal{D} )\) will be (or should be) uncertain when making
%predictions far away from the training data.
%The expectation considers all possible dynamics models which prevents the policy optimisation from
%exploiting innacuracies in the model.
%This approach has no guarantees for exploration in the general case.
%However, under specific dynamics and reward structures (e.g. PILCO) this objective can achieve sublinear regret.
%\todo{need to double check sublinear regret statement. And give a reference}
%\textbf{Posterior sampling}
%\cite{osbandWhyPosteriorSampling2017,osbandMoreEfficientReinforcement2013}
%\begin{align} \label{eq-posterior-sampling}
%\policy_{i+1}^{\text{PS}} = \arg \max_{\policy \in \policyDomain} \left[ J(\transitionFn, \policy) \right] \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i})
%\textbf{Hallucinated upper confidence RL}
%A more theoretically grounded exploration strategy is UCRL \citep{jakschNearoptimal2010}, which optimises joinly over
%policies and models inside the set
%\(\mathcal{M} = \{ f \mid | f(s,a) - \mu_{i}(s, a) | \leq \beta_{i} \Sigma_{i}(s, a) \quad \forall s, a \in \mathcal{S} \times \mathcal{A} \}\), representing all statistically plausible
%models under the posterior \(p(f(s,a) \mid \mathcal{D}_{0:i} \cup (s,a)) = \mathcal{N}(f(s,a) \mid \mu_{i}(s,a), \Sigma_{i}(s,a))\) at episode \(i\).
%This strategy is given by,
%\begin{align} \label{eq-ucrl}
%\policy_{i+1}^{\text{UCRL}} = \arg \max_{\policy \in \policyDomain} \max_{\transitionFn \in \mathcal{M}} J(\transitionFn, \policy).
%This strategy optimises an optimistic policy over the set of plausible dynamics models.
%Although this joint optimisation is intractable in general,
%\cite{curiEfficient2020} proposed a practical alternative which is detailed in \cref{sec-hucrl}.
%\textbf{MPC vs policy learning}
%It is worth noting that the strategies in \cref{eq-greedy,eq-posterior-sampling,eq-ucrl} can be used with both model predictive control (MPC)
%techniques, such as the cross entoropy method (CEM), and model-free RL techniques, such as soft actor-critic (SAC).
%In this work we are interested in how we can use \(p(f \mid \mathcal{D})\) to alleviate some of the issues in model-based RL,
%for example, model bias and the exploration-exploitation trade-off.
%\todo{show how to get new $\dualParam{1}$ and $\dualParam{2}$ in Train dynamics line of \cref{alg-mbrl-fast-updates}}
%\begin{algorithm}[!t]
%\caption{Model-based RL with fast updates}\label{alg-mbrl-fast-updates}
%\begin{algorithmic}[1]
%  \Require Start state $\state_{0}$, initial data set $\dataset_{0}$, dynamics posterior $p(\transitionFn \mid \dataset_{0})$ (inc. dual parameters $\dualParam{1}, \dualParam{2}$), policy $\policy_{0}$
%    % ${p(\state_{\timeInd+1} \mid \singleInput, \dataset_{0})}$}
%\For{$i  \in \{1, 2, \ldots, \text{num episodes} \}$}
%    \State Reset the system to $\state_{0}$ and reset trajectory buffers $\bm\tau_{t} = \emptyset \ \forall t$
%    \For{$t  \in \{1, 2, \ldots, \text{num steps} \}$}
%      % \State Execute policy $\policy_{i}(\state_{t})$ (\cref{eq-fast-update-mpc}) in environment
%      \State Use \cref{eq-fast-update-mpc} to collect data $\bm\tau_{t} = \bm\tau_{t-1} \cup (\state_{t}, \policy_{i}(\state_{t}), \transitionFn(\state_{t}, \policy^{\text{fast}}_{i}(\state_{t})), r_{t+1})$
%      % \State Append transition $\state_{t}, \action_{t}, \state_{t+1}, r_{t+1})$ to trajectory $\tau_{i}$
%      % \State $\tau_{i+1} = \{\state_{j}, \action_{j}, \state_{j+1}, r_{j+1}) \}_{j=0}^{t}$
%      %\State {\color{blue}Update dynamics $p(\transitionFn \mid \dataset_{0:i} \cup \tau_{i+1})$}
%      \State {\color{blue}Update dynamics posterior using \cref{eq-dual-update-svgp}, i.e. fast update}
%      % \begin{align}
%      % \dualParam{1}^{t+1} &\leftarrow \dualParam{1}^{t} +  \nabla_{\meanParam{1}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))} \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right] \\
%      % \dualParam{2}^{t+1} &\leftarrow \dualParam{2}^{t} +  \nabla_{\meanParam{2}} \mathbb{E}_{q_{\inducingVariable}(\latentFn(\state_{t}, \action_{t}))}  \left[ \log p(\state_{t+1} \mid \latentFn(\state_{t}, \action_{t}) ) \right]
%      % \end{align}}
%    \EndFor
%    \State Update data set $\dataset_{0:i} = \dataset_{0:i-1} \cup \tau$
%    \State Train dynamics $p(\transitionFn \mid \dataset_{0:i}) \leftarrow \text{update\_dynamics}(\dataset_{0:i}, p(\transitionFn \mid \dataset_{0:i-1}))$
%    \State Improve policy $\pi^{\text{fast}}_{i+1} \leftarrow \text{update\_policy}(p\left(\transitionFn \mid \dataset_{0:i}), \dataset_{0:i} \right)$
%\EndFor
%\end{algorithmic}
%\end{algorithm}
%\subsubsection{Fast updates}
%In this section we extend these fast updates to environment's with high dimensional state spaces and large data sets.
%% Our method draws on the connection between BNNs and GPs and formulates a function space SVGP posterior given
%Our method uses a BNN dynamic model and draws on the connection between BNNs and GPs
%\citep{khanApproximate2019} to formulate a function space SVGP posterior,
%where we can apply the fast updates from \cref{eq-dual-update-svgp}.
%At a high-level, we first use Laplace's approximation to obtain a weight space posterior for our BNN.
%We then linearise our BNN around the optimal parameters and interpret it as a GP.
%Finally, we formulate a lower rank approximation of this GP posterior (i.e. a SVGP posterior) using inducing variables.
%% formulates a function space SVGP posterior by drawing on the connection between BNNs and GPs.
%The strategies in \cref{eq-greedy,eq-posterior-sampling,eq-hucrl} do not update the dynamic model during an episode.
%A better approach would be to update the posterior at every time step during an episode, for example,
%\begin{subequations}
%\begin{align} \label{eq-fast-update-mpc}
%  \policy_{i+1}^{\text{greedy}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
%\E_{p(\transitionFn \mid \dataset_{0:i})} \left[J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) \right] + \stateValueFn(\state_{\Horizon+1}) \\
%  \policy_{i+1}^{\text{PS}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}}
%J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \transitionFn \sim p(\transitionFn \mid \dataset_{0:i} \cup \bm\tau_{t}) \\
%  \policy_{i+1}^{\text{UCRL}}(\state) &= \arg \max_{\action_{0}} \max_{\action_{1:\Horizon}} \max_{\transitionFn \in \mathcal{M}}
%J^{\Horizon}(\action_{0:\Horizon}, \transitionFn) + \stateValueFn(\state_{\Horizon+1}) \quad \text{s.t. } \mathcal{M} = \{\transitionFn(\state_{t},\action_{t}) - \mu_{i,t}(\state_{t},\action_{t}) \leq \beta_{i,t} \Sigma_{i,t}(\state_{t}, \action_{t})\} \\
%  \stateValueFn(\state) &= \mathbb{E} \left[ \sum_{t=0}^{\infty}     \discount^{t} \rewardFn(\state_{t},\action_{t}) \mid \state_{0}=\state \right] \label{eq-value-fn}
%\end{subequations}
%\begin{subequations}
%\begin{align} \label{eq-fast-update-mpc-old}
%  \policy^{\text{fast}}(\state) = \arg &\max_{\action_{0}} \max_{\action_{1}, \ldots, \action_{\Horizon}}
